### 2020-07-04 chapters/abstract.tex
SAMM

%The Abstract
%State the problem, your approach and solution, and the main contributions of the paper. Include little if any background and motivation. Be factual but comprehensive. The material in the abstract should not be repeated later word for word in the paper.

%Neste contexto, tínhamos este problema, desenvolvemos isto, avaliamos desta forma e chegamos a estas conclusões

% The problem
%Data pattern shift detection has been researched within diverse areas and application domains and refers to the process of finding patterns in data that do not conform to expected or usual behavior. Accurate and timely detection of data pattern deviations allows for immediate measures to be taken, preventing loss of income and maintaining the companies' reputation among customers. As such, many large companies take this into consideration and deploy data anomaly detection components in their systems. In this way, system administrators can proactively adjust and prevent potential service failures.

@@

%Approach/Solution and %Main contributions
In this thesis, we design a method that makes use of lightweight streaming aggregations and distribution divergence functions to alert deviations in data patterns in real-time, while in the presence of large volumes of high velocity, highly skewed and seasonal data. We develop a two-phased and two-windowed method: first we perform a batch analysis on a reference window and then a stream analysis over a sliding streaming window. We aggregate the contents of both windows using an approximate histogram aggregation based on Exponential Moving Averages. We do this for each event and for each of its fields, also denominated features in our context. We measure the divergence between both reference and sliding window histograms for each feature with the Jensen–Shannon Divergence function, but other distance functions could be used. For each feature, we find out the probability value of each divergence measure and apply the Holm-Bonferroni multiple test correction to find out which probability values are lowest and the associated features. We generate alerts based on a user-defined probability threshold, for each feature.

We evaluate our method through a series of tests, some with synthetic datasets and some with real data. We further split the tests into single and multi feature analysis. Our method accurately detected the introduced anomalies in the synthetic dataset experiments while maintaining high throughput, for single and multi feature analysis. However, experiments with real data were not as accurate. Despite not knowing the specific reasons for that, we defer further investigation to future work and formulate a set of hypothesis that might explain it and hence are worthy of pursuing next.

Our set of experiments supports the claim that sliding window aggregations and distribution divergence methods can be combined to detect data pattern shifts in streaming scenarios with constant time and memory complexity regarding window size.

\vspace*{10mm}\noindent
\textbf{Keywords}: streaming, real-time, lightweight, monitoring, volume, velocity, seasonal

>>>>

@@

%Approach/Solution and %Main contributions
In this thesis, we design a method that makes use of lightweight streaming aggregations and distribution divergence functions to alert about deviations in data patterns in real-time, while in the presence of large volumes of high velocity, highly skewed and seasonal data. We develop a two-phased and two-windowed method: first we perform a batch analysis on a reference window and then a stream analysis over a sliding streaming window. We aggregate the contents of both windows using an approximate histogram aggregation based on Exponential Moving Averages. We do this for each event and for each of its fields, also denominated features in our context. We measure the divergence between both reference and sliding window histograms for each feature with the Jensen–Shannon Divergence function, but other distance functions could be used. For each feature, we find out the probability value of each divergence measure and apply the Holm-Bonferroni multiple test correction to find out which probability values are lowest and their associated features. We generate alerts based on a user-defined probability threshold, for each feature.

We evaluate our method through a series of tests, some with synthetic datasets and some with real data. We further split the tests into single and multi-feature analysis. Our method accurately detected the introduced anomalies in the synthetic dataset experiments while maintaining high throughput, for single and multi feature analysis. However, experiments with real data were not as accurate. Despite not knowing the specific reasons for that, we defer further investigation to future work and formulate a set of hypothesis that might explain it and hence are worthy of pursuing next. Our set of experiments supports the claim that sliding window aggregations and distribution divergence methods can be combined to detect data pattern shifts in streaming scenarios with constant time and memory complexity regarding window size.

\vspace*{10mm}\noindent
\textbf{Keywords}: streaming, real-time, lightweight, monitoring, concept drift, anomaly detection

### 2020-07-04 chapters/acknows.tex
Abstract
SAMM

A lot of people contributed to this thesis. I will explicitly thank everyone, in no particular order.

@@

I thank my company supervisors, Marco Sampaio and Pedro Silva, for the advice they gave me throughout this thesis which made it possible for me to develop this project, step by step. I thank them for the hours they spent discussing with me next steps to take, experiments to conduct, new methods to try and for the remaining hours they spent analyzing the results with me. Finally, I thank them for the many hours spent reviewing this document.

@@

>>>>

A lot of people contributed to this thesis and I will explicitly thank everyone, in no particular order.

@@

I thank my company supervisors, Marco Sampaio and Pedro Silva, for the advice they gave me throughout this thesis which made it possible for me to develop this project, step by step. I thank them for the hours they spent discussing with me the next steps to take, experiments to conduct, new methods to try and for the remaining hours they spent analyzing the results with me. Finally, I thank them for the many hours spent reviewing this document.

@@

Last but certainly not least, I thank my family, friends and girlfriend for keeping me sane while I worked on this thesis during the COVID-19 lockdown.

### 2020-07-04 chapters/background.tex
Changed images
SAMM

The Venn diagram in Figure \ref{fig:stream-superset} from a blog post by Ververica \footnote{https://www.ververica.com/blog/batch-is-a-special-case-of-streaming} illustrates the relation of both processing techniques. A data stream is unbounded or infinite while a bounded data stream has a beginning and an end. Using these definitions, the concept of an unbounded data stream contains that of a bounded dataset. That is, from an infinite stream, it is possible to fix a left and right limits in order to obtain a bounded and finite dataset. This relation is visible in Figure \ref{fig:unbounded-bounded-superset} from the same blog post.

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.5]{figures/streaming-subset-batch.png}
      \caption{Stream processing as a superset of batch processing}
      \label{fig:stream-superset}
    \end{center}
\end{figure}

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.5]{figures/unbounded-superset-bounded.png}
      \caption{Unbounded data streams as a superset of bounded datasets}
      \label{fig:unbounded-bounded-superset}
    \end{center}
\end{figure}

@@

\begin{figure}[!htb]
    \begin{center}
      \hspace*{0.6in}
      \includegraphics[scale=0.35]{figures/sliding.png}
      \caption[True sliding window]{True sliding window, W=3, S=1}
      \label{fig:sliding-window} 
    \end{center}
\end{figure}

@@

\textcolor{red}{TODO change all window drawings to a not horrendous style}

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.3]{figures/stepping.png}
      \caption[Stepping window]{Stepping window, W=3, S=2}
      \label{fig:stepping-window}
    \end{center}
\end{figure}

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.3]{figures/tumbling.png}
      \caption[Tumbling window]{Tumbling window, W=S=3}
      \label{fig:tumbling-window}
    \end{center}
\end{figure}

>>>>

The Venn diagram in Figure \ref{fig:stream-superset} \cite{batch-is-a-special-case-of-streaming} illustrates the relation of both processing techniques. A data stream is unbounded or infinite while a bounded data stream has a beginning and an end. Using these definitions, the concept of an unbounded data stream contains that of a bounded dataset. That is, from an infinite stream, it is possible to fix a left and right limits in order to obtain a bounded and finite dataset. This relation is visible in Figure \ref{fig:unbounded-bounded-superset} from the same blog post.

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.5]{figures/streaming-subset-batch.png}
      \caption[Stream processing as a superset of batch processing]{Stream processing as a superset of batch processing \cite{batch-is-a-special-case-of-streaming}}
      \label{fig:stream-superset}
    \end{center}
\end{figure}

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.5]{figures/unbounded-superset-bounded.png}
      \caption[Unbounded data streams as a superset of bounded datasets]{Unbounded data streams as a superset of bounded datasets \cite{batch-is-a-special-case-of-streaming}}
      \label{fig:unbounded-bounded-superset}
    \end{center}
\end{figure}

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=1.1]{figures/sliding.pdf}
      \caption[True sliding window]{True sliding window, W=3, S=1}
      \label{fig:sliding-window} 
    \end{center}
\end{figure}

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=1.1]{figures/stepping.pdf}
      \caption[Stepping window]{Stepping window, W=3, S=2}
      \label{fig:stepping-window}
    \end{center}
\end{figure}

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=1.1]{figures/tumbling.pdf}
      \caption[Tumbling window]{Tumbling window, W=S=3}
      \label{fig:tumbling-window}
    \end{center}
\end{figure}

### 2020-07-04 chapters/introduction.tex
SAMM

We want to build a lightweight enough solution that can be integrated into existing workflows. Ensuring constant time and space complexity means that the system will remain usable for the ever-growing volumes of data. Since such a monitoring system is not mission-critical --- \textit{i.e.} the provided services don't rely on it --- the operational cost associated with it must be kept to a minimum. Having a real-time system monitoring other real-time systems consuming as many resources as the latter would be far too costly.

>>>>

We want to build a lightweight enough solution that can be integrated into existing workflows. Ensuring constant time and space complexity means that the system will remain usable for the ever-growing volumes of data. Since such a monitoring system is not mission-critical --- \textit{i.e.} the provided services do not rely on it --- the operational cost associated with it must be kept to a minimum. Having a real-time system monitoring other real-time systems consuming as many resources as the latter would be far too costly.

### 2020-07-04 chapters/method.tex
Conclusions
SAMM

To compare each feature's reference and target sliding window histogram aggregation we need a measure of divergence. We chose to use the Jensen–Shannon Divergence (JSD) \cite{JSD} but other statistical tests are possible such as Kolmogorov-Smirnov or Wasserstein \cite{EncyclopaediaMathematics}. The JSD takes as input two histograms and outputs a value between 0 and 1. The closer this value is to 0 the more similar the distributions are. On the other hand, a JSD value of 1 represents two different distributions. We chose to use the JSD metric due to its simplicity and leave as future work other possible tests.

@@

\subsection{Batch Analysis Phase} \label{sec:batch-phase}
\textcolor{red}{TODO: add some pseudocode}

The goal of the batch phase will be to build our reference aggregation for each feature and get to know the distribution of divergence or distance values between the reference and EMA-like aggregations. In other words, we:

@@

\subsection{Streaming Phase} \label{sec:stream-phase}
\textcolor{red}{TODO: add some pseudocode}

In the streaming or online phase, the system will process event by event in a true sliding window fashion (recall Section \ref{sec:windows}) and perform a change detection test periodically. This phase makes use of all of the batch phase artifacts, namely, for each feature, the reference histogram, the distribution of distance values and the last sample's histogram.

>>>>

To compare each feature's reference and target sliding window histogram aggregation we need a measure of divergence. We chose to use the Jensen–Shannon Divergence (JSD) \cite{JSD} but other statistical tests are possible such as Kolmogorov-Smirnov or Wasserstein \cite{EncyclopaediaMathematics}. The JSD takes as input two histograms and outputs a value between 0 and 1. The closer this value is to 0 the more similar the distributions are. On the other hand, a JSD value of 1 represents two different distributions. We chose to use the JSD metric due to its simplicity and because it was used in previous work successfully \cite{SAMM}, leaving as future work other possible tests.

@@

\subsection{Batch Analysis Phase} \label{sec:batch-phase}
The goal of the batch phase will be to build our reference aggregation for each feature and get to know the distribution of divergence or distance values between the reference and EMA-like aggregations. In other words, we:

@@

\subsection{Streaming Phase} \label{sec:stream-phase}
In the streaming or online phase, the system will process event by event in a true sliding window fashion (recall Section \ref{sec:windows}) and perform a change detection test periodically. This phase makes use of all of the batch phase artifacts, namely, for each feature, the reference histogram, the distribution of distance values and the last sample's histogram.

### 2020-07-04 chapters/problem-statement.tex
SAMM

\section{The Problem}
Many real-time stream monitoring systems are static once deployed in a production environment. The engineers of those systems configure them under the assumption that future data flowing through the system follows roughly the same distribution as previously seen data. They do so consciously, to the best of their knowledge and available tools, keeping in mind that in the future they may need to reconfigure the system. Thus, even though the initial configuration of the system may be one of the best fits, over time, due to data pattern shifts, the initially deployed static system's performance gradually deteriorates. The problem at hand is to determine when to reconfigure the system, \textit{e.g.} a Machine Learning model, based on an analysis of the drifts in the stream of data.

@@

\begin{itemize}
    \item \textbf{Low memory consumption:} need for a low memory footprint system that avoids linear growth relative to the sliding window size used

    \item \textbf{Low time complexity:} need for a time-efficient method that updates the sliding window aggregation and raises alerts in constant time

    \item \textbf{Fixed reference period:} the reference window must be kept the same throughout runtime

    \item \textbf{Sliding window maintainability:} possibility to evict old events and insert new ones while updating the aggregation state

    \item \textbf{Explainable alerts:} have an interpretable measure of divergence to understand why an alert was raised
\end{itemize}

>>>>

\section{The Problem}
Many real-time stream monitoring systems are static once deployed in a production environment. These systems are configured \textit{a priori} and make assumptions about future streaming data based on the observable past events. The problem is that if these assumptions no longer hold in the future, the stream monitoring systems' performance decays. Thus, the problem at hand is to determine when to reconfigure the system based on an analysis of the drifts in the stream of data. For example, consider a Machine Learning (ML) model that monitors a data stream of credit card transactions and detects fraud. The ML model trains on a reference period and learns from this training period, \textit{i.e.}, makes assumptions based on the analyzed data. In streaming, throughout time, the data patterns will change and the assumptions made will no longer hold (\textit{e.g.}, buying patterns change on holidays), which leads to a decay in model performance. Our objective is to alert data pattern shifts. Our motivation is doing it so that system administrators can reconfigure the system before the system's performance decays. In this example, system reconfiguration is tantamount to model retraining.

@@

\begin{itemize}
    \item \textbf{Low memory consumption:} need for a low memory footprint system that avoids linear growth relative to the sliding window size used;

    \item \textbf{Low time complexity:} need for a time-efficient method that updates the sliding window aggregation and raises alerts in constant time;

    \item \textbf{Fixed reference period:} the reference window must be kept the same throughout runtime;

    \item \textbf{Sliding window maintainability:} possibility to evict old events and insert new ones while updating the aggregation state;

    \item \textbf{Explainable alerts:} have an interpretable measure of divergence to understand why an alert was raised.
\end{itemize}

### 2020-07-04 chapters/sota.tex
SAMM

Univariate point outlier detection methods are further broken down into three categories: model-based, density-based and histogram-based (Figure \ref{fig:point-outlier-taxonomy} \cite{Blazquez-Garcia-Review-Anomaly-Detection}) .
\begin{figure}[!htb]
  \begin{center}
    \includegraphics[scale=1]{figures/taxonomy-point-outlier-uni.png}
    \caption{Point outlier detection in univariate time-series taxonomy}
    \label{fig:point-outlier-taxonomy}
  \end{center}
\end{figure}

@@

\begin{figure}[!htb]
  \begin{center}
    \includegraphics[scale=0.8]{figures/taxonomy-subsequence-outlier-uni.png}
    \caption{Subsequence outlier detection in univariate time-series taxonomy}
    \label{fig:subsequence-outlier-taxonomy}
  \end{center}
\end{figure}

@@

\subsubsection{A two window paradigm algorithm for change detection}
Kifer \emph{et al.} propose that detecting change in data streams can be reduced to testing if two windows have different underlying distributions \cite{Kifer-Detecting-Change}. The proposed method uses two windows, a reference \textit{W\textsubscript{1}} and a sliding one \textit{W\textsubscript{2}}. Both windows are tuple-based, have size \textit{k} and the sliding window is a true sliding one (recall Section \ref{sec:windows} and the expression \ref{math:windows}). The reference window \textit{W\textsubscript{2}} works as a \textit{reference of normality} and contains the first \textit{k} points of the stream that occurred after the last detected change.

@@

%\subsubsection{Automatic Model Monitoring for Data Streams}
%ALSO a 2 WINDOW MODEL

@@

As discussed in Section \ref{sec:back-swag-algs}, a sliding window aggregation algorithm allows the computation of an exact or approximate aggregation over a sliding window. We have presented Recalculate-From-Scratch (RFS) and Subtract-On-Evict (SOE) as the two most basic generic stream processing algorithms. In this Section we analyze other more sophisticated SWAG algorithms that fit different use-cases, restraining the set of computable aggregations to certain families, as defined in Table \ref{tbl:aggregations-properties}.

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.6]{figures/daba-ds.png}
      \caption{DABA data structure}
      \label{fig:daba-ds}
    \end{center}
\end{figure}

>>>>

Univariate point outlier detection methods are further broken down into three categories: model-based, density-based and histogram-based (Figure \ref{fig:point-outlier-taxonomy}) .
\begin{figure}[!htb]
  \begin{center}
    \includegraphics[scale=1]{figures/taxonomy-point-outlier-uni.png}
    \caption[Point outlier detection in univariate time-series taxonomy]{Point outlier detection in univariate time-series taxonomy \cite{Blazquez-Garcia-Review-Anomaly-Detection}}
    \label{fig:point-outlier-taxonomy}
  \end{center}
\end{figure}

@@

\begin{figure}[!htb]
  \begin{center}
    \includegraphics[scale=0.8]{figures/taxonomy-subsequence-outlier-uni.png}
    \caption[Subsequence outlier detection in univariate time-series taxonomy]{Subsequence outlier detection in univariate time-series taxonomy \cite{Blazquez-Garcia-Review-Anomaly-Detection}}
    \label{fig:subsequence-outlier-taxonomy}
  \end{center}
\end{figure}

@@

\subsubsection{A two window paradigm algorithm for change detection} \label{kifer}
Kifer \emph{et al.} propose that detecting change in data streams can be reduced to testing if two windows have different underlying distributions \cite{Kifer-Detecting-Change}. The proposed method uses two windows, a reference \textit{W\textsubscript{1}} and a sliding one \textit{W\textsubscript{2}}. Both windows are tuple-based, have size \textit{k} and the sliding window is a true sliding one (recall Section \ref{sec:windows} and the expression \ref{math:windows}). The reference window \textit{W\textsubscript{2}} works as a \textit{reference of normality} and contains the first \textit{k} points of the stream that occurred after the last detected change.

@@

\subsubsection{SAMM: Automatic Model Monitoring for Data Streams}

Sampaio et al. present SAMM \cite{SAMM}, an automatic model monitoring system for data streams. Similarly to the method presented in Section \ref{kifer}, SAMM uses two windows: the reference window R and the target window T. Window T contains the last $n_t$ elemnts and window R the elements of a reference period, which is prior to T. SAMM has two main components that interest us: the one responsible for computing the signal and the one that defines the signal threshold.

The Machine Learning (ML) model being monitored outputs a series of scores for each transaction. The authors build two histograms: one with the model scores for the reference window R and another for the target window T. The signal is a measure of similarity between both histograms $H_R$ and $H_T$. The authors considered using the Kolmogorov-Smirnov, Kuiper and Anderson-Darling test but ultimately used the Jensen-Shannon Divergence (JSD) \cite{JSD} to measure similarity between both histograms. The JSD outputs a value between 0 and 1, with totally different histograms being assigned a value of 1. The signal is then computed by applying the JSD metric to both histograms $H_R$ and $H_T$ at each new event.

To compute the threshold for the JSD signal, the authors maintain an histogram of observed JSD values during streaming. To efficiently maintain the JSD histogram, they devise an algorithm called SPEAR which stands for Streaming Percentiles EstimAtoR. SPEAR is linear in time and space complexity regarding the number of histogram bins, which is a small and fixed constant. This way, for a new JSD value measured between the histogram $H_R$ and histogram $H_T$, they compare it with the histogram and alert if above a certain percentile (\textit{e.g.}, the 99th percentile).

\subsubsection*{Method classification}
SAMM can take uni or multivariate time-series as input but performs a univariate analysis. This method is also a two-windowed method that measures the difference between reference and target sliding windows. The alerts produced report the entire target window as anomalous. According to the taxonomy presented in Figure \ref{fig:subsequence-outlier-taxonomy}, we classify this method as a dissimilarity-based univariate subsequence outlier detection method.

\subsubsection*{Time complexity}
For each new event, SAMM updates the target window T, updates the target histogram $H_T$, computes the JSD between $H_T$ and $H_R$, checks if this value is above a certain percentile and finally updates the histogram of JSDs with the new one.

Maintaining the target window, \textit{i.e.}, evicting old events and inserting new ones, updating the target histogram $H_T$, computing the JSD between $H_T$ and $H_R$ and checking if it is above a given percentile are all done in constant time. Updating the JSD histogram and dinamically resizing the bins with the SPEAR algorithm takes $O(n)$ time with $n$ as the number of bins. Because the number of bins is small and constant, the update of the JSD histogram is also done in constant time.

Overall, SAMM can process each event in constant time and is suitable for data stream monitoring.

\subsubsection*{Space complexity}
SAMM keeps in memory a reference window, a target window, a reference histogram, a target histogram and a JSD histogram. The histograms can have a small and fixed number of bins so they are not the dominant factor contributing to SAMM's space complexity. Instead, because SAMM keeps two windows in memory, it stores all the events belonging to them. Assuming $n_t$ as the size of target window and $n_r$ as the size of the reference window, SAMM has $O(n_r + n_t)$ space complexity.

\subsubsection*{Applicability to our Hypothesis}
SAMM was designed to work for small time periods. Hence, for the authors, keeping the reference and target windows in memory was no issue. However, in our solution, we need sublinear time and space complexities to handle large windows of data. This implies we can not directly use SAMM to solve our problem.

However, SAMM has interesting properties we can use in our final solution. First, SAMM also uses a two-window paradigm: a reference and a target sliding one. This is similar to the method seen in Section \ref{kifer}, which may indicate this is a valid and tested approach to follow. Additionally, SAMM aggregates the contents of both windows as histograms and utilizes a statistical divergence test, the Jensen-Shannon Divergence, to measure the similarity (or dissimilarity) between both. This gives them a measure of divergence which they use to raise alerts, which is another great idea to test. Finally, and contrarily to the previous method (Section \ref{kifer}), SAMM does not simply threshold this divergence value: it builds a distribution of divergence values and measures percentiles for new event's divergence values. This allows a user to easier define a threshold: instead of specifying a threshold between 0 and 1 for the JSD value, the user defines only a probability value, \textit{e.g.}, alert when the probability for a JSD value is equal or less than 1\% (percentile 99th).

Even though SAMM is not directly applicable in our context, it provides us with valid and promissing ideas to test.

@@

As discussed in Section \ref{sec:back-swag-algs}, a sliding window aggregation algorithm allows the computation of an exact or approximate aggregation over a sliding window. We want to find an aggregation that is suitable to encode our reference and streaming periods so we avoid keeping the entire sliding window in memory. Furthermore, we need an efficient algorithm to incrementally maintain this aggregation. We have presented Recalculate-From-Scratch (RFS) and Subtract-On-Evict (SOE) as the two most basic generic stream processing algorithms. In this Section we analyze other more sophisticated SWAG algorithms that fit different use-cases, restraining the set of computable aggregations to certain families, as defined in Table \ref{tbl:aggregations-properties}.

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.6]{figures/daba-ds.png}
      \caption[DABA data structure]{DABA data structure \cite{Tangwongsan-DABA}}
      \label{fig:daba-ds}
    \end{center}
\end{figure}

### 2020-07-04 chapters/validation.tex
SAMM

\subsection{Single Feature Analysis}
As an initial step, we started by validating our system using single-feature datasets before moving to multi-feature scenarios to facilitate system validation, considering the complexities of multi-feature datasets and the problem of multiple test correction. In this section we validate our results for single-feature synthetic datasets.

@@

\subsection{Multi Feature Analysis}
Before moving to real data, we performed one last experiment, using synthetic data but this time performing a multi-feature analysis. Table \ref{tbl:multi-feat-ref-dataset-distros} shows the underlying generating distributions and parameters for each of the four features ($x_1$, $x_2$, $x_3$ and $x_4$) in the reference multi-feature dataset R6. Figures \ref{fig:timeseries-r6-x1}, \ref{fig:timeseries-r6-x2}, \ref{fig:timeseries-r6-x3} and \ref{fig:timeseries-r6-x4} show the reference time-series for features $x_1$, $x_2$, $x_3$ and $x_4$ on the reference dataset R6, respectively.

>>>>

\subsection{Single-Feature Analysis}
As an initial step, we started by validating our system using single-feature datasets before moving to multi-feature scenarios to facilitate system validation, considering the complexities of multi-feature datasets and the problem of multiple test correction. In this section we validate our results for single-feature synthetic datasets.

@@

\subsection{Multi-Feature Analysis}
Before moving to real data, we performed one last experiment, using synthetic data but this time performing a multi-feature analysis. Table \ref{tbl:multi-feat-ref-dataset-distros} shows the underlying generating distributions and parameters for each of the four features ($x_1$, $x_2$, $x_3$ and $x_4$) in the reference multi-feature dataset R6. Figures \ref{fig:timeseries-r6-x1}, \ref{fig:timeseries-r6-x2}, \ref{fig:timeseries-r6-x3} and \ref{fig:timeseries-r6-x4} show the reference time-series for features $x_1$, $x_2$, $x_3$ and $x_4$ on the reference dataset R6, respectively.
